---
title: "This Guy, Elmore, Made This"
author: "Elmore Wallace"
output: flexdashboard::flex_dashboard
---


```{r,message=FALSE,warning=FALSE,echo=FALSE}


```


AAPL: Stock Price Trends {.storyboard}
=========================================

### **AAPL: Stock Price with 10 and 20 moving average, MACD at Bottom** {data-commentary-width=200}

```{r, eval=TRUE, include=FALSE, fig.width=10,fig.height=7}
library(quantmod)
getSymbols("AAPL", src = "yahoo")
chartSeries(AAPL,
            subset = '2017-12::2018',
            show.grid = TRUE,
            time.scale = NULL,
            log.scale = FALSE,
            bar.type = "ohlc")
  addSMA(n = 50, on = 1, overlay = TRUE, col = "blue")
  addSMA(n = 20, on = 1, overlay = TRUE, col = "red")
  addMACD(fast = 12, slow = 26, signal = 9)
```  


```{r}
addRSI(n = 14, maType = "EMA", wilder = TRUE)
```

```

*** 

**Summary**   
   
* Let me tell you some stuff about AAPL.   
* It may be overpriced, but is trending very strong, especailly after the last few months.
   
**Observations**   
   
* Would Recommend something else.
* It's applie.
 

### **AAPL: Another Graphic** Candle stick + BBands + CCI {data-commentary-width=200}

```{r, eval=TRUE, include=FALSE, fig.width=10,fig.height=7}
chartSeries(AAPL, theme = 'white', subset = '2017-12::2018')
  addBBands()
```

```{r}
addCCI()
```



*** 

**Summary**   
   
* You like this?
   
**Observations**   
   
* Things have been observed
 

### **AAPL: Key Financial Ratios** Key financial info  {data-commentary-width=200}

```{r,fig.width=10,fig.height=7, eval = TRUE}


```

*** 

**Summary**   
   
* 
   
**Observations**   
   
* 


### **AAPL: Look at Dis Graph** I makes anoder won {data-commentary-width=200}

```{r,fig.width=10,fig.height=8}

plot(1:100)

```

*** 

**Summary**   
   
* 
   
**Observations**   
   
* 



AAPL: Key Financial Ratios {.storyboard}
=========================================

### Financial Ratios

```{r,fig.width=12,fig.height=5, eval = TRUE}

library(tidyquant)
AAPLFinancial <-
  tq_get("AAPL", "key.ratios")

AAPL1 <- 
  AAPLFinancial$data[[1]]

AAPL2 <- 
  AAPLFinancial$data[[2]]

AAPL3 <-
  AAPLFinancial$data[[3]]

AAPL4 <-
  AAPLFinancial$data[[4]]

AAPL5 <-
  AAPLFinancial$data[[5]]

AAPL6 <-
  AAPLFinancial$data[[6]]

AAPL7 <-
  AAPLFinancial$data[[7]]

AAPL1 %>%
  ggplot(aes(x = date, y = value)) +
  facet_wrap(~category, ncol = 5, scales = "free") +
  geom_line() +
  labs(title = "AAPL: Financial Ratios 2008 to 2018",
       subtitle = "Enjoy",
       y = "Free Y Scale",
       x = "Date by Year") +
  theme_tq(base_size = 6, base_family = "")

```

*** 

Some commentary about Frame 1.

### Profitability Ratios

```{r,fig.width=12,fig.height=5, eval = TRUE}
AAPL2 %>%
  # filter(category %in% c("fish", "bob"), sub.section %in% c())
  ggplot(aes(x = date, y = value)) +
  facet_wrap(~category + sub.section, ncol = 5, scales = "free" ) +
  geom_line() +
  labs(title = "AAPL: Profitability Ratios",
       y = "Free Y Scale",
       x = "Date by Year") +
  theme_tq(base_size = 6)

```

### Growth Ratios

```{r,fig.width=12,fig.height=5, eval = TRUE}
AAPL3 %>%
  ggplot(aes(x = date, y = value)) +
  facet_wrap(~category + sub.section, ncol = 5, scales = "free" ) +
  geom_line() +
  labs(title = "AAPL: Growth Ratios",
       y = "Free Scale Y",
       x = "Date by Year") +
  theme_tq(base_size = 6)
```

### Cash Flow Ratios

```{r,fig.width=12,fig.height=5, eval = TRUE}
AAPL4 %>%
  filter(sub.section == "Cash Flow Ratios") %>%
  ggplot(aes(x = date, y = value)) +
  facet_wrap(~category, nrow = 2, scales = "free") +
  geom_line() +
  labs(title = "AAPL: Cash Flow Ratios",
       subtile = "Data From Yahoo Finance",
       y = "Free Scale Y",
       x = "Date by Year") +
  theme_tq(base_size = 8)
```

### Financial Health Ratios

```{r,fig.width=24,fig.height=10, eval = TRUE}
AAPL5 %>%
  ggplot(aes(x = date, y = value)) +
  facet_wrap(~category + sub.section, nrow = 5, scales = "free" ) +
  geom_line() +
  labs(title = "AAPL:Financial Health Ratios",
       y = "Free Y Scale",
       x = "Date by Year") +
  theme_tq(base_size = 7)
```

### Efficiency Ratios

```{r,fig.width=12,fig.height=5, eval = TRUE}
AAPL6 %>%
  filter(sub.section == "Efficiency") %>%
  ggplot(aes(x = value, y = date)) +
  facet_wrap(~category, nrow = 4, scales = "free") +
  geom_line() +
  labs(title = "AAPL: Efficiency Ratios",
       subtile = "Enjoy",
       y = "Free Scale Y",
       x = "Date by Year") +
  theme_tq(base_size = 10)
```

### Valuation Ratios

```{r,fig.width=12,fig.height=5, eval = TRUE}
AAPL7 %>%
  filter(sub.section == "Valuation Ratios") %>%
  ggplot(aes(x = date, y = value)) +
  facet_wrap(~category, nrow = 4, scales = "free") +
  geom_line() +
  labs(title = "AAPL: Valuation Ratios",
       subtile = "Enjoy",
       y = "Free Scale Y",
       x = "Date by Year") +
  theme_tq(base_size = 10)
```


Data Tables {.storyboard}
=========================================

### Stock Price data

```{r, fig.width=12, fig.height=7, eval = TRUE}

library(DT)
datatable(AAPL, options = list(pageLength = 5))

```

Economic Data {.storyboard}
=========================================

### Consumer Price Index
```{r, fig.width=12, fig.height=7, eval = TRUE}
CPI <-
  tq_get(x = c("CPIAUCSL"),
         get = "economic.data", 
         from = "2000-01-01", 
         to = "2018-01-01")

CPI %>%
  ggplot(aes(x = date, y = price)) +
  geom_line(color = "blue", size = 1) +
  labs(title = "Consumer Price Index for All Urban Consumers: All Items (CPIAUCSL)",
       subtitle = "Index 1982 - 1984 = 100 | Monthly",
       y = "Index 1982 - 1984 = 100",
       x = "Source: U.S. Bureau of Labor Statistics via FRED") +
  theme_tq()
```

### Real Gross Domestic Product
```{r, fig.width=12, fig.height=7, eval = TRUE}
RGDP <-
  tq_get(x = c("GDPC1"),
         get = "economic.data",
         from = "2000-01-01",
         to = "2018-01-01")

RGDP %>%
  ggplot(aes(x = date, y = price)) +
  geom_line(color = "blue", size = 2) +
  labs(title = "Real Gross Domestic Product (GDPC1)",
       subtitle = "Billions of Chained 2009 Dollars, Quarterly",
       y = "Billions of Chained 2009 Dollars",
       x = "Source: US Bureau of Economic Analysis via FRED") +
  theme_tq()
```

### Civilian Unemployment Rate
```{r, fig.width=12, fig.height=7, eval = TRUE}
UnEmploy <- 
  tq_get(x = c("UNRATE"), 
         get = "economic.data",
         from = "2000-01-01",
         to = "2018-01-01")

UnEmploy %>%
  ggplot(aes(x = date, y = price)) +
  geom_line(color = "blue", size = 1) +
  labs(title = "Civilian Unemployment Rate (UNRATE)",
       subtitle = "Percent | Monthly",
       x = "Source: U.S. Bureau of Labor Statistics via FRED",
       y = "Percent") +
  theme_tq()
```

### Industrial Production Index
```{r, fig.width=12, fig.height=7, eval = TRUE}
IndustrialProduction <-
  tq_get(x = c("INDPRO"),
         get = "economic.data",
         from = "2000-01-01",
         to = "2018-01-01")

IndustrialProduction %>%
  ggplot(aes(x = date, y = price)) +
  geom_line(color = "blue", size = 1) +
  labs(title = "Industrial Production Index",
       subtitle = "Index 2012 = 100 | Monthly",
       x = "Source: Board of Governors of the Federal Reserve System (US) via FRED",
       y = "Index 2012 = 100") +
  theme_tq()
```

### Nonfarm Payrolls
```{r, fig.width=12, fig.height=7, eval = TRUE}
Nonfarm <-
  tq_get(x = c("PAYEMS"),
         get = "economic.data",
         from = "2000-01-01",
         to = "2018-01-01")

Nonfarm %>%
  ggplot(aes(x = date, y = price)) +
  geom_line(color = "blue", size = 1) +
  labs(title = "All Employees: Total Nonfarm Payrolls (PAYEMS)",
       subtitle = "Thousands of Persons | Monthly",
       y = "Thousands of Persons",
       x = "Source: U.S. Bureau of Labor Statistics via FRED") +
  theme_tq()
```

### Federal Funds Rate
```{r, fig.width=12, fig.height=7, eval = TRUE}
FF <-
  tq_get(x = c("FEDFUNDS"),
         get = "economic.data",
         from = "2000-01-01",
         to = "2018-01-01")

FF %>%
  ggplot(aes(x = date, y = price)) +
  geom_line(color = "blue", size = 1) +
  labs(title = "Effective Federal Funds Rate (FEDFUNDS)",
       subtitle = "Percent | Monthly",
       y = "Percent",
       x = "Source: Board of Governors of the Federal Reserve System via FRED") +
  theme_tq()
```