---
title: "Test Flex Two"
author: "Elmore Wallace"
output: flexdashboard::flex_dashboard
---


```{r,message=FALSE,warning=FALSE,echo=FALSE}


```


Parent Quartile Grouping {.storyboard}
=========================================

### **A: LAZ Trajectories** using Mother & Father Height Quartiles  {data-commentary-width=200}

```{r,fig.width=10,fig.height=7}

plot(1:100)

```

*** 

**Summary**   
   
* We examined different percentile binning for Mother and Father heights.  Of the three percentile groupings we examined, the quartile divisions provided the optimal uncertainty reduction in LAZ at 24 months.   
* Children were grouped based on the interaction of their parent's quartile heights.  Thus children were put into 16 groups as shown in the plot.
   
**Observations**   
   
* Mother is the most productivie of the two parents in reducing uncertainty of LAZ at 24 months.
* Having a Father that is above the 75th percentile also helps group children.
 

### **B: 24 Month Distribution** using Mother & Father Height Quartiles {data-commentary-width=200}

```{r,fig.width=10,fig.height=7}

plot(1:100)

```

*** 

**Summary**   
   
* 
   
**Observations**   
   
* 
 

### **C: LAZ Trajectories with LAZ Groupings** using Mother & Father Height Quartiles  {data-commentary-width=200}

```{r,fig.width=10,fig.height=7}

plot(1:100)

```

*** 

**Summary**   
   
* 
   
**Observations**   
   
* 


### **D: 24 Month Distribution with LAZ Groupings** using Mother & Father Height Quartiles {data-commentary-width=200}

```{r,fig.width=10,fig.height=8}

plot(1:100)

```

*** 

**Summary**   
   
* 
   
**Observations**   
   
* 



Birth Weight Change Grouping {.storyboard}
=========================================

### Frame 1

```{r,fig.width=10,fig.height=7}


```

*** 

Some commentary about Frame 1.


Diarrhea Count Grouping {.storyboard}
=========================================


